Initial Analysis

### 2020-07-23 Scripts/Initial_Analysis.Rmd
Trying to get the rounded map and included VIcky's data to compare results with Teh and Sumaila

@@

  # Total catch/Revenue shapefile
  World_sf_si_land <- World_land_sf %>%
    st_transform(crs = 4326) %>% # 4326
    st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
    left_join(Value_Trans_Country, by ="fishing_entity") %>% 
    filter(Variable %in% Variable_Selected)

  # Get the NA's to be grey
  Grey_land <- World_land_sf %>%  
    filter(!NAME_EN %in% World_sf_si_land$NAME_EN)

@@

  Map <- ggplot() +
    geom_sf(data = World_sf_si_land,
            aes(fill = reorder(Bins_Plot,Value)), 
            colour = "grey80",
            size = 0.1) +
    geom_sf(data = World_sf_si,
            aes(fill =  reorder(Bins_Plot,n_trans_spp)),
            colour = "grey20",
            size = 0.1) + # n_trans_spp or Bins
    geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
    scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
                                    "#00A08A",#"#00A08A", #green
                                    "#F2AD00",#"#F2AD00", # Yellow
                                    "#F98400",#"#F98400", #Orange
                                    "#FF0000"#,"#FF0000" #Red
    ),
    na.translate = F
    ) +
    ggtheme_map() +
    # Transboundary labels
    annotate("text", 
             x =(c(-85.5,-30,25,81,136)+5),
             y = -93.5,
             label = Labels_Trans, 
             color="black", 
             size=3, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Revenue labels
    annotate("text", 
             x =(c(-85.5,-31,20,75,131)+5),
             y = -110,
             label = Labels, 
             color="black", 
             size=3, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Legend Titles
    annotate("text", 
             x =-180,
             y = -93.5,
             label = "Transboundary Spp. (n)", 
             color="black", 
             size=3, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x =-180,
             y = -110,
             label = Map_Label,
             color="black", 
             size=3, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    theme(
      legend.box.margin = margin(t = -54, l = 130),
      legend.text = element_blank(),
    ) +
    guides(fill = guide_legend(nrow = 1))

@@

@@

# Load Land shapefile
World_land_sf <- rnaturalearth::ne_countries(scale = 'medium', returnclass = c("sf")) %>% 
  st_transform(crs = "+proj=eck4") %>%
  rename(fishing_entity = name) %>% 
  mutate(
    fishing_entity = gsub("Russia", "Russian Federation",fishing_entity),
    fishing_entity = gsub( "United States of America", "USA",fishing_entity),
    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
    fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
    fishing_entity = gsub("Dem. Rep. Congo", "Congo, R. of",fishing_entity),
    fishing_entity = ifelse(fishing_entity=="Congo", "Congo (ex-Zaire)",paste(fishing_entity))
  )

@@

# Load it!
World_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = "+proj=eck4")

@@

# Entity Area (e.g. Mexico = Pacific EEZ + Atalntic EEZ)
Entity_Area <- World_sf %>% 
  as.data.frame() %>% 
  left_join(Clean_Results_Trans,
            by = "eez_name") %>% 
  group_by(fishing_entity) %>% 
  summarise(Size_Entity = sum(Area_km2))

@@

SAU_Tim_Data <- fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>% 
  mutate(value = value*1.62)

@@

@@

# Transboundary Species shapefile
World_sf_si <- World_sf %>%
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
  left_join(Transboundary_Spp, by ="eez_name")# %>%

>>>>

ggtheme_map <- function(base_size = 9, Region = "NA") {

  theme(text             = element_text(#family = "Helvetica",
    color = "gray30", size = base_size),
    plot.title       = element_text(size = rel(1.25), hjust = 0, face = "bold"),
    panel.background = element_blank(),
    panel.border     = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "transparent"),
    strip.background =element_rect(fill = "transparent"),
    strip.text.x = element_text(size = 18, colour = "black",face= "bold.italic", angle = 0),
    axis.line        = element_blank(), # element_line(colour = "grey30", size = .5))
    axis.ticks       = element_blank(),
    axis.text        = element_blank(),
    axis.title       = element_blank(),
    legend.key       = element_rect(colour = NA, fill = NA, size = 4),
    legend.position = "bottom",
    legend.key.width =unit(5,"line")
  )
}

@@

  # Total catch/Revenue shapefile
  World_sf_si_land <- World_land_sf %>%
    # st_transform(crs = 4326) %>% # 4326
    st_transform(crs = "+proj=eck4") %>%
    st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
    left_join(Value_Trans_Country, by ="fishing_entity") %>% 
    filter(Variable %in% Variable_Selected)

  # Get the NA's to be grey
  Grey_land <- World_land_sf %>%  
    filter(!fishing_entity %in% World_sf_si_land$fishing_entity)

@@

  Map <- ggplot() +
    geom_sf(data = World_sf_si_land,
            aes(fill = reorder(Bins_Plot,Value)), 
            colour = "grey80",
            size = 0.1) +
    geom_sf(data = World_sf_si,
            aes(fill =  reorder(Bins_Plot,n_trans_spp)),
            colour = "grey20",
            size = 0.1) + # n_trans_spp or Bins
    geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
    scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
                                    "#00A08A",#"#00A08A", #green
                                    "#F2AD00",#"#F2AD00", # Yellow
                                    "#F98400",#"#F98400", #Orange
                                    "#FF0000"#,"#FF0000" #Red
    ),
    na.translate = F
    ) +
    ggtheme_map() +
    # Transboundary labels
    annotate("text", 
             # x =(c(-85.5,-30,25,81,136)+5),
             # y = -93.5,
             x =(c(-85083333,-30000000,25000000,81000000,13600000)),
             y = -9350000,
             label = Labels_Trans, 
             color="black", 
             size=3, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Revenue labels
    annotate("text", 
             # x =(c(-85.5,-31,20,75,131)+5),
             # y = -110,
             x =(c(-85083333,-30000000,25000000,81000000,13600000)),
             y = -1100000,
             label = Labels, 
             color="black", 
             size=3, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Legend Titles
    annotate("text", 
             # x =-180,
             # y = -93.5,
             x =-18000000,
             y = -9350000,
             label = "Transboundary Spp. (n)", 
             color="black", 
             size=3, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             # x =-180,
             # y = -110,
             x =-18000000,
             y = -1100000,
             label = Map_Label,
             color="black", 
             size=3, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    theme(
      # legend.box.margin = margin(t = -54, l = 130),
      legend.text = element_blank(),
    ) +
    guides(fill = guide_legend(nrow = 1))

@@

# Conuntry Names relation

# matching_country_names <- my_path("D","Spatial","matching_names.csv", read = T) %>% 
#   mutate(eez_name = ifelse(is.na(eez_name),sf_eez_name,eez_name))

@@

# Load Land shapefile
World_land_sf <- rnaturalearth::ne_countries(scale = 'medium', returnclass = c("sf")) %>% 
  st_transform(crs = "+proj=eck4") %>%
  # st_transform(crs = 4326) %>% # 4326
  rename(fishing_entity = name) %>% 
  mutate(
    fishing_entity = gsub("Russia", "Russian Federation",fishing_entity),
    fishing_entity = gsub( "United States", "USA",fishing_entity),
    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
    fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
    fishing_entity = gsub("Dem. Rep. Congo", "Congo, R. of",fishing_entity),
    fishing_entity = ifelse(fishing_entity=="Congo", "Congo (ex-Zaire)",paste(fishing_entity))
  )

@@

# Load it!
World_sf <- World_sf st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = "+proj=eck4")
  # st_transform(crs = 4326) # 4326

@@

# Entity Area (e.g. Mexico = Pacific EEZ + Atalntic EEZ)
Entity_Area <- World_sf %>% 
  as.data.frame() %>% 
  left_join(Clean_Results_Trans,
            by = "eez_name") %>% 
  group_by(fishing_entity,OBJECTID) %>% 
  summarise(Size_Entity = sum(Area_km2))

@@

SAU_Tim_Data <- fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) #%>% 
  # mutate(value = value*1.62)

# Read SAU non-reconstructed catch data from 2006 for comparrisonwith Sumaila
# SAU_Vicky_Data <- fread(paste(my_path("D"),"Distribution/ReportCatch_FEYrEEZTaxon_2010_14.csv", sep =""))

SAU_Vicky_Data <- fread(paste(my_path("D"),"Distribution/ReportCatch_FEYrEEZTaxon_2005_09.csv", sep =""))

@@

### New estimates!!!

# Filter SAU data for only those sampled species

SAU_Sampled_Data <- Clean_sau_eez_fes %>%
  group_by(fishing_entity,fishing_entity_id,eez_name) %>% 
  summarise(n=n()) %>% 
  left_join(SAU_Tim_Data, by = "fishing_entity_id") %>% 
  left_join(Exploited_Species) %>% 
  filter(!is.na(taxon_name)) %>% 
  clean_names() %>% 
  group_by(fishing_entity_id,taxon_key) %>% 
  summarise_at(c("catch","value"),
               mean,na.rm=T) %>% 
  gather("Variable","Value",catch:value)

x <- Tresholded_T_Data %>% 
  select(taxon_key,eez_name) %>% 
  group_by(taxon_key,eez_name) %>% 
  summarise(n=n()) %>% 
  ungroup() %>% 
  select(-n) %>% 
  left_join(Clean_sau_eez_fes,
            by = "eez_name") %>% 
  left_join(SAU_Sampled_Data,
            by = c("taxon_key","fishing_entity_id")) %>% 
  # filter(eezid != 0) %>%
  group_by(Variable) %>%
  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
  mutate(Per_sampled = Total_Trans/Total_SAU_Vicky*100)

```{r comparriosn_wtih_teh}

# Average data for the last 10 years

SAU_Global_Vicky <- SAU_Vicky_Data %>% 
  filter(#eezid != 0,
         year == 2006) %>%
  group_by(fishing_entity_id,taxon_key,eezid) %>% 
  summarise_at(c("sumcatch"),
               mean,na.rm=T)

## Get the total of global data
Total_SAU_Vicky <- sum(SAU_Global_Vicky$sumcatch,na.rm = T)

Summary_Trans_vicky <- Tresholded_T_Data %>% 
  select(taxon_key,eez_name) %>% 
  group_by(taxon_key,eez_name) %>% 
  summarise(n=n()) %>% 
  ungroup() %>% 
  select(-n) %>% 
  left_join(Clean_sau_eez_fes,
            by = "eez_name") %>% 
  left_join(SAU_Global_Vicky,
            by = c("taxon_key","fishing_entity_id")) %>% 
  # filter(eezid != 0) %>%
  group_by() %>%
  summarise(Total_Trans = sum(sumcatch, na.rm=T)) %>% 
  mutate(Per_sampled = Total_Trans/Total_SAU_Vicky*100);Summary_Trans_vicky

@@

# Transboundary Species shapefile
World_sf_si <- World_sf %>%
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
  left_join(Transboundary_Spp, by ="eez_name") %>% 
  st_transform(crs = "+proj=eck4")
  # st_transform(crs = 4326)
